Influences of GDP in the U.S

### 2022-11-10 Manuscript/manuscript.tex
commit

>>>>

(cite GDP PARAdox) researches the critism behind GDP's influence in economies. They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare. 
Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries." (cite PARADOX)
They also touch on how government agencies and politicians strive to avoid low GDP. When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (cite PARADOX)
